High-accuracy neutron diffusion calculations based on integral transport theory

### 2019-12-04 docs/EPJP2019/response/response.tex

We hope that the Editor and the reviewer find the revised manuscript satisfactory and recommend it for publication.

%--------------------------------------------------------------
% LETTERS ENDS HERE ******************************************
\closing{\mbox{Sincerely yours on behalf of all the co-authors,}}

%---------------------------------------------------------------------------------------	-
\newpage

\textbf{Reviewer \#1}
\\ \\
% --------------------------------------------------------------------------------------
\textit{Please re-read the whole paper to check the language and the punctuation. Some sentences are very concise and could be expanded a little for clarity.}
\\ \\
\revised{The manuscript underwent a thorough examination of the language and punctuation, and some sentences were elaborated for clarity.}
\\ \\
% --------------------------------------------------------------------------------------
\textit{I have a concern on which the Authors may want to comment. Formula (3) becomes problematic where the gradient of the flux is small, which is usually the zone where diffusion works better.}
\\ \\
\revised{This is correct. Ronen did not elaborate on this issue in his technical note from 2004. Theoretically, both the numerator and the denominator should vanish at the same location, since both are accurate expressions for the neutron current at this location (where the flux gradient is weak). We did not try to find the analytic limit of this expression for $D$, however we assume that this ratio between two expressions, which vanish at the same location, approaches some constant value.\\ \\ Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}. The (more accurate) surface current $J_{tr}$, calculated by integral expression, is written as the sum of the surface current calculated by diffusion, $J_D$, plus a correction $\delta J$. Hence, when the current vanishes, the correction $\delta J$ vanishes. Moreover, the correction is written as in Eq. (21), avoiding the potential divergence resulting from division by zero. This comment was added to the text.}
\\ \\
% --------------------------------------------------------------------------------------
\textit{I do not think it would be too hard work to report more results. For instance, I think it would be nice to see the effect of the physical size of the domain, to better detect and evidence the effect of the boundary. This would add a lot to the value of the paper.}
\\ \\
\revised{An entire benchmark was added to the results section. The chosen benchmark is a one-dimensional highly heterogeneous core representing a BWR core. The sensitivity of the method to the slab width, especially at the boundaries, will be studied in future work, along with additional effects emanate from the boundaries conditions.}
\\ \\
% --------------------------------------------------------------------------------------
\textit{In the abstract: I suggest to avoid saying that the results match "extremely well" the reference... while this is true for the eigenvalue, it may be questionable for the flux near the boundary, where effects should be more deeply investigated. Maybe "well" is already enough.}
\\ \\
\revised{Fixed.}
\\ \\

@@

% --------------------------------------------------------------------------------------
\textit{Page 6, To me the title of subsection 3.2 is not correct (there is no such a thing as "integral currents". Should it rather be something like "evaluation of the currents by the integral form of the transport equation"? I suggest also to change the caption of Fig. 2 accordingly.}
\\ \\
\revised{Fixed.}
\\ \\

\newpage

% --------------------------------------------------------------------------------------
\textit{Since the whole section consider the multigroup formulation, at line 6 to be consistent I suggest to change $J(x,E)$ to $J_g(x)$. }
\\ \\
\revised{Fixed.}
\\ \\
% --------------------------------------------------------------------------------------
\textit{Page 7, About boundary conditions: how is the extrapolated distance chosen with vacuum? For instance, with a Mark or a Marshak approach or according to other recipes? And, in any case, what is the value assumed for the calculations? Furthermore, the Authors should also comment on the problem of the need to update the extrapolated distance since it is in general related to the diffusion coefficient (e.g. 2D in Marshak BC). In this respect, the meaning of the sentence in line 53 and 54 is not clear to me.}
\\ \\
\revised{The extrapolated distance for vacuum is set to $\zeta=2.13D$ (according to Lamarsh 1966). The Marshak boundary conditions are reproduced by $\zeta=2D$). The values assumed for the homogeneous slab calculations are 1.3367 and 0.5459 cm for the fast and thermal groups, respectively. \\ \\
As for the need to update the extrapolated distance, it should be noted that the diffusion coefficient remains constant throughout the calculation, and so is the extrapolated distance. Only $\delta D$ is recalculated. Note that the correction in our numerical scheme is not by $D = D_0 + \delta D$ nor by $D = \delta D$. The correction is actually implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.   }
\\ \\
% --------------------------------------------------------------------------------------
\textit{page 8, The statement about boundary conditions should be clarified at line 40. What does "they are constant for each energy group" mean? If it means that the same extrapolated distance is assumed for both groups, the Authors should consider to make a more consistent assumption of group-dependent extrapolated distances. The effect of the choice of the BC is not insignificant, especially for optically thin systems. It could be interesting to see the effect of the different choices.}
\\ \\
\revised{The above statement was changed to: "Void boundary conditions are used at the edges of the slab, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$.".\\ \\We completely agree that the choice of BC matters and it affects the numerical solutions, since BC should adequately describe the physical problem. We also speculate that the slow convergence rate of the flux (by RM iterations) near the boundaries is linked to the choice of proper BC. We intend to study this issue in the near future. }
\\ \\
% --------------------------------------------------------------------------------------
\textit{In Table 1 units must be indicated.}
\\ \\
\revised{Fixed.}
\\ \\

@@

\newpage

% --------------------------------------------------------------------------------------
\textit{At line 50, please change "w/" with "with". At line 55, please change "w/o" with "without". The use of such contractions (such as "\&" above) is not advisable in a scientific paper. I suggest to make these changes throughout the whole paper.}
\\ \\
\revised{Fixed.}
\\ \\
% --------------------------------------------------------------------------------------
\textit{At line 60, it is advisable to expand on "the corrected diffusion current exhibit(s)non-trivial behaviour near the boundary". Can it be related to BC?}
\\ \\
\revised{Fig. 5 and any reference to it are omitted from the revised manuscript.}
\\ \\
% --------------------------------------------------------------------------------------
\textit{General comment on the Figures: it would be nice to explicitly identify the quantities in the graphs rather than letting the reader struggle to interpret them from the legend.}
\\ \\
\revised{We have added (where possible) explicit text indications on the figure itself to distinguish between the different quantities.}
\\ \\
% --------------------------------------------------------------------------------------
\textit{In Fig. 8: is there any explanation for the sign change in some curves?}
\\ \\
\revised{The following text was added to the manuscript:\\ The initial diffusion solution is smoother than the transport one. Hence, as can be seen in Fig. 4 (in the original and revised ms), the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary. The Ronen iterations "push" the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary. Hence, $\phi^{k-1}$ is smaller in the center and larger at the boundary comparing to $\phi^(k)$.	This effect of the Ronen iterations produces less smooth flux shape with steeper gradients comparing to the diffusion solution. }
\\ \\
% --------------------------------------------------------------------------------------
\textit{Suggestion for further work: it should not be too difficult to study a heterogeneous configuration, since the Ronen method naturally leads to a non-homogeneous system, to see how the Ronen method adapts to interfaces, where strong gradients of the flux might appear.}
\\ \\
\revised{T}
\\ \\

### 2019-12-04 docs/EPJP2019/Gross-EPJP-2019.tex
Final revision for comments from Daniele and Roy

%
% ---------------------------------------------------
\subsection{Boundary conditions}
\label{sec:BC}
A generalized form for the boundary condition (at the left) follows as
\begin{equation}\label{eq:BC}
J_D(x=0) = -D_0\frac{\phi_0}{\Delta x_0/2 + \zeta} \,\, ,
\end{equation} 
where $\zeta$ is the extrapolation length in case of vacuum. The Marshak boundary conditions are reproduced by $\zeta=2D$, but the more accurate value $\zeta\approx 2.13D$ is
taken to match transport with better agreement~\cite{Lamarsh-1966}. Reflection can be reproduced by $\zeta\rightarrow\infty$, whereas the condition of zero-flux is realized by $\zeta=0$. 
%
The quantity $\delta J$ at the boundary takes the simpler form of $\delta J = -\delta D_{-1/2}\phi_0$, without dividing by the spatial width, since no particular extrapolation length is appropriate for the correction. The expression for the right boundary is straightforward, implying a non-negative current. One should recall that the diffusion coefficient remains constant throughout the calculation, and so is the extrapolated distance. Only $\delta D$ is recalculated and the correction of the diffusion coefficient is implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.

@@

Two one-dimensional test cases are considered, homogeneous and heterogeneous. The reference solutions are calculated using a Python3 discrete ordinates ($S_N$) code with $N=16$~\cite{Lewis-1984}. The diffusion solutions and the Ronen iterations are produced using original codes developed in Pyhton3. All thresholds are set to 1E-6 and no (over/under)-relaxation is done. The initial diffusion coefficient is set to $D=(3\sigma_{tr})^{-1}=(3\sigma)^{-1}$. Void boundary conditions are used (extrapolated distance) at the edges of the slab and they are constant for each energy group.

@@

A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:fluxes} (left panel) for half-slab. The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_N$ flux is also shown in Fig.~\ref{fig:fluxes} (upper right panel). The deviation from the reference solution is decreased by the Ronen iterations from approximately 20\% near the boundary and 1\% at the slab center to 2\% and 0\%, respectively.

@@

\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[b]{.44\linewidth}
		% First figure
		\includegraphics[width=\linewidth]{Sn_Diff_RM_Tomatis2011.pdf}
		%\caption{A tall figure}
	\end{subfigure}
	~
	\begin{subfigure}[b]{.54\linewidth}
		% Second figure
		~\includegraphics[width=0.97\linewidth]{flx_err_Tomatis2011_400_250.pdf}
		%\caption{A short figure}		
		%\vspace{2ex}
		% Third figure
		\includegraphics[width=\linewidth]{dD_Tomatis2011_400_250it.pdf}
		%\caption{A short figure}
	\end{subfigure}
	\caption{Left: Comparison of the fluxes as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$). Right, up: Deviation of the fluxes with respect to the reference solution. Right, down: The RM correction terms ($\delta D$). Results shown here after 250 Ronen iterations.}
	\label{fig:fluxes}
\end{figure}

@@

\begin{figure}[h!]
	% convergence
	\centering
	\includegraphics[width=0.4\linewidth]{convergence.pdf}
	\caption{Convergence of the flux (max deviation) and the criticality
		eigenvalue.}
	\label{fig:conv}
\end{figure}
The RM correction terms ($\delta D$) along the plane are shown in Fig.~\ref{fig:fluxes} (lower right panel). It is clear that the diffusion correction assumes zero values at the slab center and exhibit non-trivial behavior near the boundary. The convergence of the flux (max deviation) and the criticality eigenvalue are shown in Fig.~\ref{fig:conv}. While the eigenvalue converges within a few iterations, the flux exhibit slow convergence near the boundaries. The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta\phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%]. The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab is shown in Fig.~\ref{fig:conv3}.

% convergence
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_1.pdf}
	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_2.pdf}
	\caption{The spatial flux convergence between two successive Ronen iterations for the left half slab, according to $\Delta\phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].}
	\label{fig:conv2}
\end{figure}

% convergence
\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_1_sn.pdf}
	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_2_sn.pdf}
	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab.}
	\label{fig:conv3}
\end{figure}

%
% ---------------------------------------------------
\subsection{Heterogeneous case}
\label{subsec:heterog}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.32\linewidth]{Sn_Diff_RM_core_1.pdf}
	\includegraphics[width=0.32\linewidth]{Sn_Diff_RM_core_2.pdf}
	\includegraphics[width=0.32\linewidth]{Sn_Diff_RM_core_3.pdf}
	\caption{Fast and thermal flux for each core using standard diffusion ($D_0$), Ronen method (RM) and S16 reference solution. Vertical grid lines are located at assemblies interfaces. RM results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
	\label{fig:hetero-flux}
\end{figure}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.6\linewidth]{flx_err_diff_C1.pdf}
	\includegraphics[width=0.6\linewidth]{flx_err_diff_C2.pdf}
	\includegraphics[width=0.6\linewidth]{flx_err_diff_C3.pdf}
	\caption{Fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions for each core. Vertical grid lines are located at assemblies interfaces. RM results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
	\label{fig:hetero-flux-dev}
\end{figure}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.6\linewidth]{RM_dD1_100it_8_22_728.pdf}
	\includegraphics[width=0.6\linewidth]{RM_dD2_100it_8_22_728.pdf}
	\caption{Behavior of the Ronen method correction factor $dD$ along the core, for the fast and thermal fluxes. Vertical grid lines are located at assemblies interfaces, results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
	\label{fig:Dcoef}
\end{figure}

@@

The Ronen Method was first proposed for better estimates of the diffusion coefficient by calculating the current with a higher-order transport operator and a known best-estimate neutron flux. This yielded an iterative scheme leading to new flux distributions solved by a diffusion solver but with additional (spatially) corrected diffusion terms, driving the diffusion solution to that of the integral transport equation. The direct resolution of the integral equation would imply the inversion of large matrices, with poor control of their conditioning. The solution of the diffusion equation, on the other hand, offers many numerical advantages, e.g., speed and robustness. Nonetheless, the same current can be enforced in the discretized form of the diffusion equation as suggested by the CMFD, which avoids the numerical issues resulting from small flux gradients. This is the option adopted in this study.

>>>>

%
% ---------------------------------------------------
\subsection{Boundary conditions}
\label{sec:BC}
A generalized form for the boundary condition (at the left) follows as
\begin{equation}\label{eq:BC}
J_D(x=0) = -D_0\frac{\phi_0}{\Delta x_0/2 + \zeta} \,\, ,
\end{equation} 
where $\zeta$ is the extrapolation length in case of vacuum. The Marshak boundary conditions are reproduced by $\zeta=2D$, but the more accurate value $\zeta\approx 2.13D$ is taken to match transport with better agreement~\cite{Lamarsh-1966}. Reflection can be reproduced by $\zeta\rightarrow\infty$, whereas the condition of zero-flux is realized by $\zeta=0$. 
%
The quantity $\delta J$ at the boundary takes the simpler form of $\delta J = -\delta D_{-1/2}\phi_0$, without dividing by the spatial width, since no particular extrapolation length is appropriate for the correction. The expression for the right boundary is straightforward, implying a non-negative current. One should recall that the diffusion coefficient remains constant throughout the calculation, and so is the extrapolated distance. Only $\delta D$ is recalculated and the correction is actually implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.

@@

Two one-dimensional test cases are considered, homogeneous and heterogeneous. The reference solutions are calculated using a Python3 discrete ordinates ($S_N$) code with $N=16$~\cite{Lewis-1984}. The diffusion solutions and the Ronen iterations are produced using original codes developed in Pyhton3. All thresholds are set to 1E-6 and no (over/under)-relaxation is done. The initial diffusion coefficient is set to $D=(3\sigma_{tr})^{-1}=(3\sigma)^{-1}$. Void boundary conditions are used at the edges of the slab, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$.

@@

A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for half-slab. The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_N$ flux is also shown in Fig.~\ref{fig:slab-fluxes-dev}. The corresponding Ronen method correction factors $\delta D$ are shown in Fig.~\ref{fig:slab-RM-corr-factor}.

The deviation from the reference solution is decreased by the Ronen iterations from approximately 20\% near the boundary and 1\% at the slab center to 2\% and 0\%, respectively.

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.65\linewidth]{Sn_Diff_RM_Tomatis2011.pdf}
	\caption{Comparison of the fluxes as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$). Results shown here after 250 Ronen iterations.}
	\label{fig:slab-fluxes}		
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.65\linewidth]{flx_err_Tomatis2011_400_250.pdf}
	\caption{Deviation of the fluxes with respect to the reference solution after 250 Ronen iterations.}
	\label{fig:slab-fluxes-dev}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.65\linewidth]{dD_Tomatis2011_400_250it.pdf}
	\caption{The Ronen method correction factors ($\delta D$). Results shown here after 250 Ronen iterations.}
	\label{fig:slab-RM-corr-factor}
\end{figure}

@@

\begin{figure}[h!]
	% convergence
	\centering
	\includegraphics[width=0.4\linewidth]{convergence.pdf}
	\caption{Convergence of the flux (max deviation) and the criticality
		eigenvalue.}
	\label{fig:conv}
\end{figure}

The RM correction terms ($\delta D$) along the plane are shown in Fig.~\ref{fig:slab-RM-corr-factor}. It is clear that the diffusion correction assumes zero values at the slab center and exhibit non-trivial behavior near the boundary. The convergence of the flux (max deviation) and the criticality eigenvalue are shown in Fig.~\ref{fig:conv}. While the eigenvalue converges within a few iterations, the flux exhibit slow convergence near the boundaries. The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta\phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%]. The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab is shown in Fig.~\ref{fig:conv3}.

% convergence
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_1.pdf}
	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_2.pdf}
	\caption{The spatial flux convergence between two successive Ronen iterations for the left half slab, according to $\Delta\phi = (\phi^{(k-1)}-\phi^{(k)})/\phi^{(k-1)}$ [\%].}
	\label{fig:conv2}
\end{figure}

% convergence
\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_1_sn.pdf}
	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_2_sn.pdf}
	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab.}
	\label{fig:conv3}
\end{figure}

Notice the change of sign in the flux convergence $\Delta \phi$ in Fig.~\ref{fig:conv2} between the center (negative) and the boundary (positive) of the slab. The initial diffusion solution is smoother than the transport one. Hence, as can be seen in Fig.~\ref{fig:slab-fluxes}, the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary. The Ronen iterations "push" the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary. Hence, $\phi^{(k-1)}$ is smaller in the center and larger at the boundary comparing to $\phi^{(k)}$. This effect of the Ronen iterations produces less smooth flux shape with steeper gradients comparing to the diffusion solution.
%
% ---------------------------------------------------
\subsection{Heterogeneous case}
\label{subsec:heterog}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.46\linewidth]{Sn_Diff_RM_core_1.pdf}
	\includegraphics[width=0.46\linewidth]{Sn_Diff_RM_core_2.pdf}
	\includegraphics[width=0.46\linewidth]{Sn_Diff_RM_core_3.pdf}
	\caption{Fast and thermal flux for each core using standard diffusion ($D_0$), Ronen method (RM) and S16 reference solution. Vertical grid lines are located at assemblies interfaces. RM results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
	\label{fig:hetero-flux}
\end{figure}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.65\linewidth]{flx_err_diff_C1.pdf}
	\includegraphics[width=0.65\linewidth]{flx_err_diff_C2.pdf}
	\includegraphics[width=0.65\linewidth]{flx_err_diff_C3.pdf}
	\caption{Fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions for each core. Vertical grid lines are located at assemblies interfaces. RM results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
	\label{fig:hetero-flux-dev}
\end{figure}

@@

\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.65\linewidth]{RM_dD1_100it_8_22_728.pdf}
	\includegraphics[width=0.65\linewidth]{RM_dD2_100it_8_22_728.pdf}
	\caption{Behavior of the Ronen method correction factor $dD$ along the core, for the fast and thermal fluxes. Vertical grid lines are located at assemblies interfaces, results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
	\label{fig:Dcoef}
\end{figure}

@@

The Ronen Method was first proposed for better estimates of the diffusion coefficient by calculating the current with a higher-order transport operator and a known best-estimate neutron flux. This yielded an iterative scheme leading to new flux distributions solved by a diffusion solver but with additional (spatially) corrected diffusion terms, driving the diffusion solution to that of the integral transport equation. The direct resolution of the integral equation would imply the inversion of large matrices, with poor control of their conditioning. The solution of the diffusion equation, on the other hand, offers many numerical advantages, e.g., speed and robustness.

The relation in Eq.~\eqref{eq:RM-it-1D-slab} becomes problematic where the gradient of the flux is small, which is usually the zone where diffusion works better. Ronen did not elaborate on this issue in his technical note from 2004. Theoretically, both the numerator and the denominator should vanish at the same location, since both are accurate expressions for the neutron current where the flux gradient is weak. We hypothesize that this ratio, between two expressions which tend to zero at the same location, approaches some constant value since there exist a diffusion coefficient at that location.

Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}. The (more accurate) surface current $J_{\texttt{tr}}$, calculated by integral expression, is written as the sum of the surface current calculated by diffusion, $J_\texttt{D}$, plus a correction $\delta J$. Hence, when the current vanishes, the correction $\delta J$ vanishes as well. Moreover, the correction is written as in Eq.~\eqref{eq:JD-dJ}, avoiding the potential divergence resulting from division by zero.

%Nonetheless, the same current can be enforced in the discretized form of the diffusion equation as suggested by the CMFD, which avoids the numerical issues resulting from small flux gradients. This is the option adopted in this study.
